### 2020-04-04 Thesis/pmonads.tex
Corrections.

Since a monoid in a monoidal category $\mathcal X$ is the same thing as a lax monoidal functor from the unit category into $\mathcal X$, the definition of a monad on a category $\C$ (i.e., a monoid in $[\C,\C]$) may be generalized to that of a \emph{lax action} \cite{LaxActions} of a monoidal category $\X$ on $\C$; i.e., a lax monoidal functor $\X \to [\C,\C]$ (so that a monoid in $\C$ is a lax action of the unit category on $\C$).

@@

Suppose that a monoidal category $\X$ acts on a category $\C$.
\begin{definition}
  A \emph{\Mellies morphism} from $a$ to $b$ is one of the form
  \[
    a \to x.b\,,
    \]
  for some object $x$ of $\X$.
\end{definition}

\begin{definition}
  Given \Mellies morphisms $f$ from $a$ to $b$ and $g$ from $b$ to $c$ given by
  \begin{mathpar}
    \tilde{f} \from a \to x.b
    \and
    \tilde{g} \from b \to y.c\,,
  \end{mathpar}
  their \emph{\Mellies composition} is given by the composite
  \[
    a \xrightarrow{\tilde f}
    x.b \xrightarrow{x.\tilde g}
    x.y.c \xrightarrow{m_{x,y,c}}
    (x\tensor y).c\,,
    \]
  which is a \Mellies morphism from $a$ to $c$.
  \label{DefMelliesComposition}
\end{definition}
\begin{definition}[\cite{ThesisForDays}]
  Let $\X$ be a monoidal category and let 
  \[
    F,G\from \X \to \Set
    \]
  be functors.  
  Then the \emph{Day convolution} of $F$ and $G$ is a functor
  \[
    F \tensor_{\text{Day}} G \from \X \to \Set
    \]
  given by the coend
  \[
    (F \tensor_{\text{Day}} G)(x) = \int^{y,z\from \X} F(y) \times G(z) \times \X(y\tensor z,x)\,.
    \]
  This makes $[\X,\Set]$ into a monoidal category (the monoidal unit is the functor $\X(I,\blank)\from \X \to \Set$).
  \label{DefDayConvolution}
\end{definition}

\begin{definition}[\cite{MelliesCategory}]
  Given a lax action of a monoidal category $\X$ upon a category $\C$, the \emph{\Mellies category} of the action is an $[\X,\Set]$-enriched category $\Mell_\X\C$ whose objects are the objects of $\C$ and where the hom objects are given by
  \[
    \Mell_\X\C(a,b)(x) = \C(a,x.b)\,.
    \]
  The composition is given by the natural transformation
  \begin{IEEEeqnarray*}{Cl}
    & (\Mell_\X\C(a,b) \tensor_{\text{Day}} \Mell_\X\C(b,c))(x)\\
    = & \int^{y,z\from \X} \C(a,y.b) \times \C(b,z.c) \times \X(y\tensor z,x) \\
    \to & \int^{y,z\from \X} \C(a,(y\tensor z).c) \times \X(y\tensor z,x) \\
    \cong & \C(a,x.c) \\
    = & \Mell_\X\C(a,c)(x)\,,
  \end{IEEEeqnarray*}
  where the arrow on the third line is induced by the \Mellies composition $\C(a,y.b) \times \C(b,z.c) \to \C(a,(y\tensor z).c)$.

@@

For our purposes, however, we will want to use a single ordinary category that captures as much as possible of the structure of the \Mellies category.
Let us assume for now that $\X$ is a small category.  
Then we have a functor
\begin{IEEEeqnarray*}{cCc}
  [\X,\Set] & \to & \Set \\
  F & \mapsto & \colim_{x\from \X} F(x)
\end{IEEEeqnarray*}
given by the colimit in $\Set$.

@@

We then conclude by changing base through this colimit functor.  
It turns out to be fairly easy to describe the resulting category directly.

\begin{definition}
  Let a monoidal category $\X$ act on a category $\C$ via a lax action.  
  Then we define a new category $\C/\X$ where
  \begin{itemize}
    \item the objects are the objects of $\C$;
    \item given objects $a,b$ of $\C$, the set of morphisms $a \to b$ is given by the colimit
      \[
        \colim_{x\from \X} \C(a,x.b)\,;
        \]
      i.e., a morphism in $\C/\X$ from $a$ to $b$ is an equivalence class of \Mellies morphisms
      \[
        a \to x.b
        \]
      in $\C$, where $x$ ranges over the objects of $\X$, and where the equivalence relation on morphisms is generated by identifying two morphisms $f\from a \to x.b$, $g \from a \to y.b$ if there is a morphism $h\from x\to y$ in $\X$ such that the following diagram commutes (we say that $h$ \emph{mediates} between $f$ and $g$);
      \[
        \begin{tikzcd}
          a \arrow[r, "f"] \arrow[dr, "g"']
            & x.b \arrow[d, "h.b"] \\
          %
            & y.b
        \end{tikzcd}
        \]
    \item composition of morphisms is via the \Mellies composition of Definition \ref{DefMelliesComposition}; and
    \item the identity $a\to a$ is given by the equivalence class corresponding to the morphism
      \[
        e_a \from a \to I.a
        \]
      in $\C$.
  \end{itemize}
  \label{DefCX}
\end{definition}

\begin{remark}
  We will not in general assume that $\X$ is a small category, as we do above, but we will assume that the colimits in Definition \ref{DefCX} do exist in $\Set$.  
  If $\X$ is a small category, then they are small colimits so they exist automatically.
  If the colimits do not exist, then we get a category that is not locally small.
\end{remark}

@@

  Lastly, we need to check that the identity we have defined is indeed an identity for the composition.  
  The following diagrams show us that the morphism $\lunit_x$ in $\X$ mediates between a \Mellies morphism $f\from a \to x.b$ and the \Mellies composite $e_a;f$, and that the morphism $\runit_x$ in $\X$ mediates between $f$ and the \Mellies composite $f;e_b$.
  \begin{mathpar}
    \begin{tikzcd}
      a \arrow[r, "f"] \arrow[d, "e_a"']
        & x.b \arrow[d, "e_{x.b}"'] \arrow[dr, "\lunit_x.b"]
          & \\
      I.a \arrow[r, "I.f"]
        & I.x.b \arrow[r, "{m_{I,x,b}}" xshift=-3pt]
          & (I\tensor x).b
    \end{tikzcd}
    \and
    \begin{tikzcd}
      a \arrow[r, "f"]
        & x.b \arrow[r, "x.e_b"] \arrow[dr, "\runit_x.b"']
          & x.I.b \arrow[d, "{m_{x,I,b}}"] \\
      %
        &
          & (x\tensor I).b
    \end{tikzcd}
    \and
    \qedhere
  \end{mathpar}
\end{proof}

@@

We will be meeting the following `factorization result', analogous to the corresponding result for Kleisli categories that we met in the previous section.
If $f \from a \to x.b$ is a morphism in $\C$ then the corresponding \Mellies morphism $a \to b$ may be written as the following composite in $\C/\X$.
\[
  a \xrightarrow{Jf}
  x.b \xrightarrow{\phi_{x,b}}
  b\,.
  \]
Indeed, if we compute this composite in $\C$, then we get
\[
  a \xrightarrow{f}
  x.b \xrightarrow{e_{x.b}}
  I.x.b \xrightarrow{\id}
  I.x.b \xrightarrow{m_{I,x,b}}
  (I\tensor x).b\,,
  \]
which is equivalent to $f$ in $\C/\X$, because $e_{x.b};m_{I,x,b}=\lunit_x.b$, so $\lunit_x$ mediates between this morphism and $f$.

@@

\begin{definition}[\cite{StreetTwoConstructions}]
  Let $\C,\D$ be bicategories.  
  A \emph{lax functor} $F\from\C \to \D$ is given by
  \begin{itemize}
    \item a map $F$ from the objects of $\C$ to the objects of $\D$;
    \item for each pair $a,b$ of objects of $\C$, a functor
      \[
        F \from \C(a,b) \to \D(F(a),F(b))\,;
        \]
    \item for each triple $a,b,c$ of objects of $\C$, a transformation 
      \[
        m_{f,g}\from F(f);F(g) \to F(f;g)
        \]
      natural in $f\from a \to b$, $g\from b \to c$; and
    \item for each object $a$ of $\C$, a $2$-cell 
      \[
        e_a\from \id_{Fa} \Rightarrow F(\id_a)\from Fa \to Fa\,;
        \]
  \end{itemize}
  such that for all tuples $a,b,c,d$ of objects and all morphisms $f\from a \to b$, $g\from b \to c$, $h \from c \to d$, the following diagrams commute.
  \begin{mathpar}
    \begin{tikzcd}[column sep=60pt]
      (F(f);F(g));F(h) \arrow[r, "{\assoc_{F(f),F(g),F(h)}}"] \arrow[d, "{m_{f,g};F(h)}"']
        & F(f);(F(g);F(h)) \arrow[d, "{F(f);m_{g,h}}"] \\
      F(f;g);F(h) \arrow[d, "{m_{f;g,h}}"']
        & F(f);F(g;h) \arrow[d, "{m_{f,g;h}}"] \\
      F((f;g);h) \arrow[r, "{F(\assoc_{f,g,h})}"]
        & F(f;(g;h))
    \end{tikzcd}
    \and
    \begin{tikzcd}
      Ff \arrow[r, "\lunit_{Ff}"] \arrow[d, "F\lunit_f"']
        & \id_{Fa} ; Ff \arrow[d, "e_a;Ff"] \\
      F(\id_a;f)
        & F\id_a;Ff \arrow[l, "{m_{\id_a,f}}"']
    \end{tikzcd}
    \and
    \begin{tikzcd}
      Ff \arrow[r, "\runit_{Ff}"] \arrow[d, "F\runit_f"']
        & Ff ; \id_{Fb} \arrow[d, "Ff;e_b"] \\
      F(f;\id_b)
        & Ff;F\id_b \arrow[l, "{m_{f,\id_b}}"']
    \end{tikzcd}
  \end{mathpar}
\end{definition}
\begin{example}
  If $\C = \BB \X$, $\D = \BB \YY$ are the delooping bicategories of monoidal categories $\X, \YY$ -- i.e., $\X$ and $\YY$ considered as bicategories with a single object -- then a lax functor $\C \to \D$ is the same thing as a lax monoidal functor $\X \to \YY$.  
\end{example}

\begin{example}
  More generally, a lax functor $F\from \BB \X \to \D$ is the same as a lax monoidal functor from $\X$ to the monoidal category of $1$-cells $F(*) \to F(*)$, where $*$ is the unique object of $\BB\X$.  
  In particular, a lax functor $1\to \Cat$ is the same thing as a monad and a lax functor $\BB\X \to \Cat$ is the same thing as a parametric monad parameterized by $\X$.
\end{example}

\begin{definition}
  Let $F \from \C \to \D$ be a lax functor of bicategories.  
  Then an \emph{oplax cocone under $F$} is given by an object $d$ of $\D$, together with $1$-cells
  \[
    l_c \from F(c) \to d
    \]
  for each object $c$ of $\C$ and $2$-cells
  \[
    \mu_h \from F(h);l_{c'} \Rightarrow l_c \from F(c) \to d
    \]
  for each $1$-cell $h\from c \to c'$ in $\C$, such that for all $2$-cells $\phi\from h' \Rightarrow h \from c \to c'$ the diagram
  \[
    \begin{tikzcd}
      F(h');l_{c'} \arrow[r, "\mu_{h'}", Rightarrow] \arrow[d, "F(\phi);l_{c'}"', Rightarrow]
        & l_c \\
      F(h);l_{c'} \arrow[ur, "\mu_h"', Rightarrow]
        &
    \end{tikzcd}
    \]
  commutes, and such that for all $h\from c \to c'$, $h' \from c' \to c''$, the diagrams
  \begin{mathpar}
    \begin{tikzcd}[column sep=60pt]
      (F(h);F(h'));l_{c''} \arrow[r, "{\assoc_{F(h),F(h'),l_{c''}}}", Rightarrow] \arrow[d, "{m_{h,h'};l_{c''}}"', Rightarrow]
        & F(h);(F(h');l_{c''}) \arrow[r, "F(h);\mu_{h'}", Rightarrow] 
          & F(h);l_{c'} \arrow[d, "\mu_h", Rightarrow] \\
      F(h;h');l_{c''} \arrow[rr, "\mu_{h;h'}", Rightarrow]
        &
          & l_c
    \end{tikzcd}
    \and
    \begin{tikzcd}
      l_c \arrow[r, "\lunit_{l_c}", Rightarrow] \arrow[d, "\id_{l_c}"', Rightarrow]
        & \id_c;l_c \arrow[d, "e_c;l_c", Rightarrow] \\
      l_c
        & F(\id_c);l_c \arrow[l, "\mu_{\id}"', Rightarrow]
    \end{tikzcd}
  \end{mathpar}
  commute.
\end{definition}

\begin{definition}[\cite{Gepner}]
  Let $F \from \C \to \D$ be a lax functor of bicategories.  
  Then a \emph{lax colimit} of $F$ is an oplax cocone $(u,k,\nu)$ under $F$ such that if $(d,l,\mu)$ is any other oplax cocone then there is a unique $1$-cell $\hat{l} \from u \to d$ such that $k_c;\hat{l}=l_c$ for each object $c$ of $\C$ and such that $\nu_h\hat{l}=\mu_h$ for any $1$-cell $h\from c \to c'$ in $\C$.
\end{definition}

@@

\begin{remark}
  The definition of a lax colimit is normally weaker than the one we have given, in that the equations $k_c;\hat l = l_c$ and $\nu_h\hat l = \mu_h$ are not required to hold exactly, but instead up to coherent isomorphism.  
  The distinction is not important for our purposes, since the lax colimits we will be considering will all satisfy our stronger definition.
\end{remark}

@@

\begin{proposition}
  Let $F,G \from \C \Rightarrow \D$ be lax functors and let $t \from F \Rightarrow G$ be an oplax natural transformation.  
  Suppose that $F$ and $G$ have lax colimits $\tilde{F}$ and $\tilde{G}$.  
  Then $t$ naturally gives rise to a lax functor $\tilde{F} \to \tilde{G}$ in a way that respects composition and identity of lax natural transformations.
  \label{PropFunctorialityOfLaxColimits}
\end{proposition}
\begin{proof}
  Composing the limiting oplax cocone $k^G\from G \to *_{\tilde{G}}$ with $t$ gives us an oplax natural transformation $F \to *_{\tilde{G}}$ and hence a unique lax functor $(t;k^G)\hat{}\from \tilde{F} \to \tilde{G}$ such that $k^F_c;(t;k^G)\hat{}=t_c;k^G_c$ and $\nu^F_h(t;k^G)\hat{}=\nu^G_h$ for all objects $c$ and morphisms $h$ in $\C$.

@@

  We therefore have
  \[
    j(h,f) = j(k_a(f);(\nu_h)_n) = j(k_a(f));j((\nu_h)_n) = l_a(f);(\mu_h)_n = \hat{l}(h, f)\,,
    \]
  and therefore $j=\hat{l}$.  
\end{proof}

>>>>

Since a monoid in a monoidal category $\mathcal X$ is the same thing as a lax monoidal functor from the unit category into $\mathcal X$, the definition of a monad on a category $\C$ (i.e., a monoid in $[\C,\C]$) may be generalized to that of a \emph{lax action} \cite{LaxActions} of a monoidal category $\X$ on $\C$; i.e., a lax monoidal functor $\X \to [\C,\C]$ (so that a monad on $\C$ is a lax action of the unit category on $\C$).

@@

Suppose that a monoidal category $\X$ acts on a category $\C$.
\begin{definition}
  A \emph{\Mellies morphism} from $a$ to $b$ is a morphism of the form
  \[
    a \to x.b\,,
    \]
  for some object $x$ of $\X$.
\end{definition}

\begin{remark}
  In what follows, the object $x$ will be part of the data of the \Mellies morphism, so a \Mellies morphism from $a$ to $b$ is a pair $(x,f)$, where $f\from a \to x.b$ is an ordinary morphism.  
  We will omit the $x$ when it is clear from the context.
\end{remark}

\begin{definition}
  Given \Mellies morphisms $f$ from $a$ to $b$ and $g$ from $b$ to $c$ given by
  \begin{mathpar}
    \tilde{f} \from a \to x.b
    \and
    \tilde{g} \from b \to y.c\,,
  \end{mathpar}
  their \emph{\Mellies composition} is given by the composite
  \[
    a \xrightarrow{\tilde f}
    x.b \xrightarrow{x.\tilde g}
    x.y.c \xrightarrow{m_{x,y,c}}
    (x\tensor y).c\,,
    \]
  which is a \Mellies morphism from $a$ to $c$.
  \label{DefMelliesComposition}
\end{definition}

Having defined our basic notion of composition, we can move on to our main constructions.
We start with some definitions that will help us navigate size issues.

\begin{definition}
  Let $\C$ be a category.  
  An \emph{ancestral set} (see \cite{AllGoodCategories}) for $\C$ is a set $\A$ of objects of $\C$ such that for any object $a$ of $\C$, there is an object $a'\in\A$ and a morphism $f \from a' \to a$.
  A \emph{descendent\footnote{This is not a typo -- \emph{descendent} is the adjectival form of the noun \emph{descendant}.} set} for $\C$ is an ancestral set for $\oppcat\C$; i.e., a set $\D$ of objects of $\C$ such that for any object $a$ of $\C$, there is an object $a'\in\D$ and a morphism $f \from a \to a'$.
\end{definition}

We are interested in (small) ancestral and descendent sets, because they help guarantee the existence of certain large limits and colimits in $\Set$.

\begin{proposition}[\cite{AllGoodCategories}]
  i) Let $J \from \X \to \Set$ be a diagram, where $\X$ has a small ancestral set $\A$.
  Then $J$ has a limit in $\Set$.

  ii) Let $J\from \YY \to \Set$ be a diagram, where $\YY$ has a small descendent set $\D$.
  Then $J$ has a colimit in $\Set$.
  \label{PropAllGoodCategories}
\end{proposition}
\begin{proof}
  (i): The limit is given by the set
  \[
    l = \left\{(\xi_a) \in \prod_{a\in A}J(a) \suchthat \forall f \from a \to x, g \from b \to x,\,J(f)(\xi_a)=J(g)(\xi_b)\right\}\,,
    \]
  where $f$ and $g$ range over all morphisms from objects in $\A$ to general objects of $\X$.

  (ii): The colimit is given by the set
  \[
    c = \sum_{d \in \D} J(d) / \sim\,,
    \]
  where $\sim$ is the equivalence relation on pairs $(d, \eta_d)$ (for $d\in \D$ and $\eta_d\in J(d)$), generated by
  \[
    \left(\exists y\from \YY, f\from d \to y,g\from e \to y \esuchthat J(f)(\eta_d) = J(g)(\eta_{e})\right) \mathrel{\Rightarrow} (d,\eta_d) \sim (e,\eta_e)\,.
    \]
  The proofs that these are indeed a limit and a colimit for the corresponding diagrams are very similar to the proofs for ordinary small limits and colimits in $\Set$.  
  However, the constructions we have made above rely on more than the fact that $\Set$ is complete and cocomplete.  
  We also need to be able to perform universal and existential quantification over large collections of objects; this corresponds to the category-theoretic fact that if we have any (possibly large) collection of monomorphisms
  \[
    A_i \to B
    \]
  in $\Set$ (for fixed $B$), then we can form their intersection (i.e., a category-theoretic pullback for the collection), and similarly that we can form the pushout of any (possibly large) collection of epimorphisms out of a set.
  See \ref{AllGoodCategories} for full details.
\end{proof}

\begin{definition}
  Let $\X$ be a monoidal category.  
  Given an object $x$ of $\X$, a \emph{tensor-descendent set for $x$} is an ancestral set for the category of elements\footnote{See the proof of Proposition \ref{PropMonoidalFunctorIsColimitOfReaderAction}.} of the functor $\X(\blank\tensor\blank,x) \from \oppcat\X \times \oppcat\X \to \Set$; i.e., a set $\D_x$ of objects of $\X$ such that for any morphism
  \[
    f \from y \tensor z \to x
    \]
  there exist $y',z'\in \D_x$ and morphisms $h \from y \to y'$, $k \from z \to z'$, $\tilde f \from y'\tensor z' \to x$ such that the following diagram commutes.
  \[
    \begin{tikzcd}
      y \tensor z \arrow[r, "h \tensor k"] \arrow[dr, "f"']
        & y' \tensor z' \arrow[d, "\tilde f"] \\
      %
        & x
    \end{tikzcd}
    \]
  We say that $\X$ is \emph{well-tensored} if every object $x$ of $\X$ has a small tensor-descendent set.
  \label{DefWellTensored}
\end{definition}

\begin{definition}[\cite{ThesisForDays}]
  Let $\X$ be a well-tensored monoidal category and let 
  \[
    F,G\from \X \to \Set
    \]
  be functors.  
  Then the \emph{Day convolution} of $F$ and $G$ is a functor
  \[
    F \tensor_{\text{Day}} G \from \X \to \Set
    \]
  given by the coend
  \[
    (F \tensor_{\text{Day}} G)(x) = \int^{y,z\from \X} F(y) \times G(z) \times \X(y\tensor z,x)\,.
    \]
  This makes $[\X,\Set]$ into a monoidal category (the monoidal unit is the functor $\X(I,\blank)\from \X \to \Set$).
  \label{DefDayConvolution}
\end{definition}

\begin{remark}
  The reason that we need well-tensoredness of $\X$ is to ensure that the coend above is a small set.  
  Indeed, let
  \[
    [y, z, a, b, f]
    \]
  be an arbitrary element of the coend (for $y,z\from \X$, $a\in F(y)$, $b\in G(z)$ and $f \from y\tensor z \to x$).  
  Given a small tensor-descendent set $\D_x$, we can find $y',z'\in \D_x$ and morphisms $h \from y \to y'$, $k \from z \to z'$ and $\tilde{f} \from y'\tensor z' \to x$ as in Definition \ref{DefWellTensored}.  
  Then we have
  \[
    [y, z, a, b, f] = [y', z', F(h)(a), F(k)(b), \tilde{f}]\,.
    \]
  It follows that the coend is a subset of the small set
  \[
    \sum_{y',z'\in \D_x} F(y') \times G(z') \times \X(y'\tensor z',x)\,,
    \]
  and is therefore itself small.

  We could alternatively have deduced this from Proposition \ref{PropAllGoodCategories}, using the fact that the coend above may be recast as a colimit indexed by the opposite of the category of elements of $\X(\blank\tensor\blank,x)$.
\end{remark}

\begin{definition}[\cite{MelliesCategory}]
  Given a lax action of a well-tensored monoidal category $\X$ upon a category $\C$, the \emph{\Mellies category} of the action is an $[\X,\Set]$-enriched category $\Mell_\X\C$ whose objects are the objects of $\C$ and where the hom objects are given by
  \[
    \Mell_\X\C(a,b)(x) = \C(a,x.b)\,.
    \]
  The composition is given by the natural transformation
  \begin{IEEEeqnarray*}{Cl}
    & (\Mell_\X\C(a,b) \tensor_{\text{Day}} \Mell_\X\C(b,c))(x)\\
    = & \int^{y,z\from \X} \C(a,y.b) \times \C(b,z.c) \times \X(y\tensor z,x) \\
    \to & \int^{y,z\from \X} \C(a,(y\tensor z).c) \times \X(y\tensor z,x) \\
    \cong & \C(a,x.c) \\
    = & \Mell_\X\C(a,c)(x)\,,
  \end{IEEEeqnarray*}
  where the arrow on the third line is induced by the \Mellies composition $\C(a,y.b) \times \C(b,z.c) \to \C(a,(y\tensor z).c)$.

@@

For our purposes, however, we will want to use a single ordinary category that captures as much as possible of the structure of the \Mellies category.
Suppose that $\X$ has, in addition, a small descendent set.
Then we have a functor
\begin{IEEEeqnarray*}{cCc}
  [\X,\Set] & \to & \Set \\
  F & \mapsto & \colim_{x\from \X} F(x)
\end{IEEEeqnarray*}
given by the colimit in $\Set$.

@@

We then conclude by changing base through this colimit functor.  
It turns out to be fairly easy to describe the resulting category directly, and we can drop the well-tensoredness condition.

\begin{definition}
  Let a monoidal category $\X$ with a small descendent set act on a category $\C$ via a lax action.  
  Then we define a new category $\C/\X$ where
  \begin{itemize}
    \item the objects are the objects of $\C$;
    \item given objects $a,b$ of $\C$, the set of morphisms $a \to b$ is given by the colimit
      \[
        \colim_{x\from \X} \C(a,x.b)\,;
        \]
      i.e., a morphism in $\C/\X$ from $a$ to $b$ is an equivalence class of \Mellies morphisms
      \[
        a \to x.b
        \]
      in $\C$, where $x$ ranges over the objects of $\X$, and where the equivalence relation on morphisms is generated by identifying two morphisms $f\from a \to x.b$, $g \from a \to y.b$ if there is a morphism $h\from x\to y$ in $\X$ such that the following diagram commutes (we say that $h$ \emph{mediates} between $f$ and $g$);
      \[
        \begin{tikzcd}
          a \arrow[r, "f"] \arrow[dr, "g"']
            & x.b \arrow[d, "h.b"] \\
          %
            & y.b
        \end{tikzcd}
        \]
    \item composition of morphisms is via the \Mellies composition of Definition \ref{DefMelliesComposition}; and
    \item the identity $a\to a$ is given by the equivalence class corresponding to the morphism
      \[
        e_a \from a \to I.a
        \]
      in $\C$.
  \end{itemize}
  \label{DefCX}
\end{definition}

\begin{remark}
  If we follow Proposition \ref{PropAllGoodCategories} exactly, then the object $x$ in the \Mellies morphism $a \to x.b$ has to be contained in the small descendent set of $\X$.  
  Instead, we shall stick to the traditional formulation of the colimit, as for small diagrams, only using Proposition \ref{PropAllGoodCategories} so that we can be sure that the colimit is a small set.
\end{remark}

@@

  Lastly, we need to check that the identity we have defined is indeed an identity for the composition.  
  The following diagrams show us that the morphism $\lunit_x$ in $\X$ mediates between a \Mellies morphism $f\from a \to x.b$ and the \Mellies composite $e_a;f$, and that the morphism $\runit_x$ in $\X$ mediates between $f$ and the \Mellies composite $f;e_b$.
  \begin{mathpar}
    \begin{tikzcd}
      a \arrow[r, "f"] \arrow[d, "e_a"']
        & x.b \arrow[d, "e_{x.b}"'] \arrow[dr, "\lunit_x.b"]
          & \\
      I.a \arrow[r, "I.f"]
        & I.x.b \arrow[r, "{m_{I,x,b}}" xshift=-3pt]
          & (I\tensor x).b
    \end{tikzcd}
    \and
    \begin{tikzcd}
      a \arrow[r, "f"]
        & x.b \arrow[r, "x.e_b"] \arrow[dr, "\runit_x.b"']
          & x.I.b \arrow[d, "{m_{x,I,b}}"] \\
      %
        &
          & (x\tensor I).b
    \end{tikzcd}
    \qedhere
  \end{mathpar}
\end{proof}

@@

@@

\begin{definition}[\cite{StreetTwoConstructions}]
  Let $\C,\D$ be bicategories.  
  A \emph{lax functor} $F\from\C \to \D$ is given by
  \begin{itemize}
    \item a map $F$ from the objects of $\C$ to the objects of $\D$;
    \item for each pair $a,b$ of objects of $\C$, a functor
      \[
        F \from \C(a,b) \to \D(F(a),F(b))\,;
        \]
    \item for each triple $a,b,c$ of objects of $\C$, a transformation 
      \[
        m_{f,g}\from F(f);F(g) \to F(f;g)
        \]
      natural in $f\from a \to b$, $g\from b \to c$; and
    \item for each object $a$ of $\C$, a $2$-cell 
      \[
        e_a\from \id_{Fa} \Rightarrow F(\id_a)\from Fa \to Fa\,;
        \]
  \end{itemize}
  such that for all tuples $a,b,c,d$ of objects and all morphisms $f\from a \to b$, $g\from b \to c$, $h \from c \to d$, the following diagrams commute.
  \begin{mathpar}
    \begin{tikzcd}[column sep=60pt]
      (F(f);F(g));F(h) \arrow[r, "{\assoc_{F(f),F(g),F(h)}}"] \arrow[d, "{m_{f,g};F(h)}"']
        & F(f);(F(g);F(h)) \arrow[d, "{F(f);m_{g,h}}"] \\
      F(f;g);F(h) \arrow[d, "{m_{f;g,h}}"']
        & F(f);F(g;h) \arrow[d, "{m_{f,g;h}}"] \\
      F((f;g);h) \arrow[r, "{F(\assoc_{f,g,h})}"]
        & F(f;(g;h))
    \end{tikzcd}
    \and
    \begin{tikzcd}
      Ff \arrow[r, "\lunit_{Ff}"] \arrow[d, "F\lunit_f"']
        & \id_{Fa} ; Ff \arrow[d, "e_a;Ff"] \\
      F(\id_a;f)
        & F\id_a;Ff \arrow[l, "{m_{\id_a,f}}"']
    \end{tikzcd}
    \and
    \begin{tikzcd}
      Ff \arrow[r, "\runit_{Ff}"] \arrow[d, "F\runit_f"']
        & Ff ; \id_{Fb} \arrow[d, "Ff;e_b"] \\
      F(f;\id_b)
        & Ff;F\id_b \arrow[l, "{m_{f,\id_b}}"']
    \end{tikzcd}
  \end{mathpar}
\end{definition}
\begin{example}
  Given a monoidal category $\X$, write $\BB \X$ for the bicategory having a single object $*$, where $\BB\X(*,*)$ is the category $\X$ and composition of $1$-cells $x,y \from * \to *$ is given by
  \[
    x;y = x \tensor y\,.
    \]
  If $\C = \BB \X$, $\D = \BB \YY$ are the delooping bicategories of monoidal categories $\X, \YY$, then a lax functor $\C \to \D$ is the same thing as a lax monoidal functor $\X \to \YY$.  
\end{example}

\begin{example}
  More generally, a lax functor $F\from \BB \X \to \D$ is the same as a lax monoidal functor from $\X$ to the monoidal category of $1$-cells $F(*) \to F(*)$.
  In particular, a lax functor $1\to \Cat$ is the same thing as a monad and a lax functor $\BB\X \to \Cat$ is the same thing as a parametric monad parameterized by $\X$.
\end{example}

\begin{definition}
  Let $F \from \C \to \D$ be a lax functor of bicategories.  
  Then an \emph{oplax cocone under $F$} is given by an object $d$ of $\D$ (called the \emph{tip} of the cocone), together with $1$-cells
  \[
    l_c \from F(c) \to d
    \]
  for each object $c$ of $\C$ and $2$-cells
  \[
    \mu_h \from F(h);l_{c'} \Rightarrow l_c \from F(c) \to d
    \]
  for each $1$-cell $h\from c \to c'$ in $\C$, such that for all $2$-cells $\phi\from h' \Rightarrow h \from c \to c'$ the diagram
  \[
    \begin{tikzcd}
      F(h');l_{c'} \arrow[r, "\mu_{h'}", Rightarrow] \arrow[d, "F(\phi);l_{c'}"', Rightarrow]
        & l_c \\
      F(h);l_{c'} \arrow[ur, "\mu_h"', Rightarrow]
        &
    \end{tikzcd}
    \]
  commutes, and such that for all $h\from c \to c'$, $h' \from c' \to c''$, the diagrams
  \begin{mathpar}
    \begin{tikzcd}[column sep=60pt]
      (F(h);F(h'));l_{c''} \arrow[r, "{\assoc_{F(h),F(h'),l_{c''}}}", Rightarrow] \arrow[d, "{m_{h,h'};l_{c''}}"', Rightarrow]
        & F(h);(F(h');l_{c''}) \arrow[r, "F(h);\mu_{h'}", Rightarrow] 
          & F(h);l_{c'} \arrow[d, "\mu_h", Rightarrow] \\
      F(h;h');l_{c''} \arrow[rr, "\mu_{h;h'}", Rightarrow]
        &
          & l_c
    \end{tikzcd}
    \and
    \begin{tikzcd}
      l_c \arrow[r, "\lunit_{l_c}", Rightarrow] \arrow[d, "\id_{l_c}"', Rightarrow]
        & \id_c;l_c \arrow[d, "e_c;l_c", Rightarrow] \\
      l_c
        & F(\id_c);l_c \arrow[l, "\mu_{\id}"', Rightarrow]
    \end{tikzcd}
  \end{mathpar}
  commute.
\end{definition}

\begin{definition}[\cite{BasicBicategories}]
  Let $(d, l, \mu)$, $(d', l', \mu')$ be oplax cocones for a lax functor $F \from \C \to \D$.  
  Then a \emph{modification of oplax cocones} $l \to l'$ is given by a collection of $2$-cells
  \[
    \delta_c \from l_c \Rightarrow l_c'
    \]
  for each object $c$ of $\C$, such that the following diagram commutes for any $1$-cell $h \from c \to c'$ in $\C$.
  \[
    \begin{tikzcd}[arrows=Rightarrow]
      F(h);l_{c'} \arrow[r, "\mu_h"] \arrow[d, "F(h);\delta_{c'}"']
        & l_c \arrow[d, "\delta_c"] \\
      F(h);l_{c'}' \arrow[r, "\mu_h'"]
        & l_c'
    \end{tikzcd}
    \]
\end{definition}

\begin{definition}[\cite{Gepner}]
  Let $F \from \C \to \D$ be a lax functor of bicategories.  
  Then a \emph{lax colimit} of $F$ is an oplax cocone $(u,k,\nu)$ under $F$ such that 
  \begin{itemize}
    \item if $(d,l,\mu)$ is any other oplax cocone under $F$ then there is a unique $1$-cell $\hat{l} \from u \to d$ such that $k_c;\hat{l}=l_c$ for each object $c$ of $\C$ and such that $\nu_h\hat{l}=\mu_h$ for any $1$-cell $h\from c \to c'$ in $\C$; and
    \item if $(d,l',\mu')$ is another oplax cocone under $F$ with tip $d$ and $\delta \from l \Rightarrow l'$ is a modification of oplax cocones, then there is a unique $2$-cell $\hat{\delta} \from \hat{l} \Rightarrow \hat{l'}$ such that $h_c;\hat{\delta}=\delta_c$ for all objects $c$ of $\C$.
  \end{itemize}
\end{definition}

@@

\begin{remark}
  Our definition of a lax colimit $(u,k,\nu)$ tells us that if $d$ is an object of $\C$, then there is an isomorphism of categories from the category $\C(u, d)$ to the category of oplax cocones under $F$ with tip $d$, with morphisms given by modifications of oplax cocones.
  As a consequence, any two lax colimits for the same diagram are uniquely isomorphic as cocones.

  There is a more usual definition of an oplax cocone, in which this isomorphism of categories is weakened to an equivalence.
  The distinction is not important for our purposes, since the lax colimits we will be considering will all satisfy our stronger definition.
\end{remark}

@@

\begin{proposition}
  Let $F,G \from \C \Rightarrow \D$ be lax functors and let $t \from F \Rightarrow G$ be an oplax natural transformation.  
  Suppose that $F$ and $G$ have lax colimits with tips $\tilde{F}$ and $\tilde{G}$.  
  Then $t$ naturally gives rise to a lax functor $\tilde{F} \to \tilde{G}$ in a way that respects composition and identity of lax natural transformations.
  \label{PropFunctorialityOfLaxColimits}
\end{proposition}
\begin{proof}
  Composing the limiting oplax cocone $k^G\from G \to *_{\tilde{G}}$ with $t$ gives us an oplax natural transformation $F \to *_{\tilde{G}}$ and hence a unique lax functor $(t;k^G)\hat{}\from \tilde{F} \to \tilde{G}$ such that $k^F_c;(t;k^G)\hat{}=t_c;k^G_c$ and $\nu^F_h(t;k^G)\hat{}=\nu^G_h$ for all objects $c$ and morphisms $h$ in $\C$.

@@

  We therefore have
  \[
    j(h,f) = j(k_a(f);(\nu_h)_n) = j(k_a(f));j((\nu_h)_n) = l_a(f);(\mu_h)_n = \hat{l}(h, f)\,,
    \]
  and therefore $j=\hat{l}$.
